Predicting sales of newly published books

### 2015-08-21 paper.tex
Descritos los 5 métodos utilizados. Closes #4
Traducido completamente (ya no queda texto en español). Closes #8
arreglos menores...

Throughout this research we collaborated with the company Trevenque Editorial\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors.

@@

The objective is finding the most appropriate forecasting method that minimizes 
the error between the forecast and the actual sales for each new book published.

@@

Once  the methods to be applied have determined as well as their execution 
parameters, they must be applied to data sets to obtain the prediction models 
for each one. Later on, the models ability must be validated on non-previously 
seen data.

\textbf{TODO:} % FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS

@@

>>>>

Throughout this research we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors.

@@

The objective is finding the most appropriate forecasting method that minimizes 
the error between the obtained forecast and the actual sales for each new book 
published.

@@

Once the methods to be applied have been chosen, they must be applied to data sets 
to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.

\textbf{TODO: FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS}

@@

\textbf{TODO: FALTA COMENTAR LOS RESULTADOS OBTENIDOS CON LOS 5 MÉTODOS.}
